---
title: "Supplementary material: Toyworld generation, Estimation and Evaluation"
author: "Fabio Ricciato, Angelo Coluccia, Marco Ramljak"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    code_folding: show
    code_download: true
    theme: sandstone
    toc: true
    toc_float: true
    number_sections: true
    fig_caption: yes
knit: (function(input_file, encoding) { out_dir <- 'docs'; rmarkdown::render(input_file,
  encoding=encoding, output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

<style>
  p.caption {
  font-size: 1em;
}
  body {
  font-size: 12pt;
}
</style>

This notebook provides supplementary material as well as the complete code for reproducing the toyworld, executing all estimators and evaluating these estimators. The toyworld is based on a semi-synthetic data generated process. For this, census data from Germany on a 100m\*100m regular grid has been used, which can be downloaded [here](https://www.zensus2011.de/DE/Home/Aktuelles/DemografischeGrunddaten.html?nn=3065474). Each element in this grid is expressed as a tile. For computation purposes only a small area of Germany was used for the toyworld, namely the area of Munich and its near surroundings. This focus area includes 160,000 tiles. The code for clipping this specific area can be found [here](https://github.com/R-ramljak/MNO_mobdensity/blob/master/Code/Munich_generate.R), which is also part of this research repository. For a mobile phone population the regular census population values are used. To mimic the mobile phone population of one mobile network operator (MNO) the population is reduced to about a third.

Furthermore, custom functions have been built and are used throughout this notebook, which can be found [here](https://github.com/R-ramljak/MNO_mobdensity/blob/master/Code/pipeline%20functions.R). In near time, these will be released within an R-package.

The notebook has three main sections: Toyworld Generation, Estimation, Evaluation.

# General Setup: Loading Packages and Custom Functions

```{r packages, message=FALSE}
# Data manipulation
library(tidyverse)
library(data.table) 

# Spatial operations
library(sf)
library(raster)
library(stars)

# Matrix operations
library(Matrix)

# MNO data handling and propagation model setup
# Credits to Prof. Martijn Tennekes https://github.com/mtennekes/mobloc
library(mobloc)

# Comparison of 2d histograms (Kantorovitch Wasserstein distance a.k.a. Earth Movers distance)
# Credits to Prof. Stefano Gualandi https://cran.r-project.org/web/packages/SpatialKWD/SpatialKWD.pdf
library(SpatialKWD)

# Output organisation and plotting support
library(ggthemes)
library(viridis)
library(ggrepel)
library(ggpointdensity)
library(scattermore)
library(grid)
library(gridExtra)
library(knitr)
library(DT)

# seed for reproducibility
set.seed(42)


# Loading Custom functions
source("pipeline functions.R")

```

# Toyworld Generation

This section is concerned with generating a toyworld that is based on the above specified focus area. After specifying the population aspect of the toyworld, the radio network will be specified.

## Toyworld Generation: Population

This subsection defines the generation of a population. As mentioned above the focus area is zoomed into the area of Munich and its near surroundings. The following chunk specifies the necessary objects to continue with the creation of a radio network in this focus area.

```{r population-data}
# data read in
munich.raw <- readRDS("Data/munich.rds")

# define raster object from focus area
munich.raster <- rasterFromXYZ(munich.raw, crs = st_crs(3035)$proj4string)

# define empty list object where all GTP objects will be stored
munich <- NULL

# define sf version of raster object
munich$area.sf <- munich.raster %>%
  st_as_stars() %>%
  st_as_sf() %>%
  mutate(centroid.geometry = st_centroid(.$geometry)) %>% 
  mutate(X.centroid = unlist(map(.$centroid.geometry, 1)),
         Y.centroid = unlist(map(.$centroid.geometry, 2))) %>% 
  dplyr::select(tile.id, pop, elevation, X.centroid, Y.centroid) %>%
  mutate(tile.id.chr = as.character(tile.id)) %>% 
  mutate(tile.id.fac = factor(tile.id.chr)) %>% 
  mutate(tile.id.num = as.numeric(tile.id.fac)) %>% 
  mutate(type = "NA") # only necessary if different tile types can be defined (urban, rural, etc...)

# regular dataframe version
munich$area.df <- munich$area.sf %>%
  st_drop_geometry()

# variable reduced dataframe version
munich$area.reduced.df <- munich$area.df %>% 
  dplyr::select(tile.id.chr, contains("centroid"))

# unionized version of focus area
munich$area.union <- munich$area.sf %>%
  st_union()

# bounding box coordinates of focus area
munich$area.bbox <- munich$area.union %>%
  st_bbox(crs = sf::st_crs(3035))

# specify raster object and tile id number
munich$area.raster <- munich.raster %>%
  raster(., layer = "tile.id")

# specify raster object and elevation value of each tile (here considered as constant)
munich$area.elevation <- munich.raster %>%
  raster(., layer = "elevation")

# number of tiles
munich$area.params[["tile.num"]] <- length(munich$area.df$tile.id)

# size of tiles
munich$area.params[["base.tile.size"]] <- as.numeric(sqrt(st_area(munich$area.sf[1,])))

# storing everything in area object
area <- munich

saveRDS(area, "workflow_objects/area.rds")
```

```{r gtp-map, fig.cap="Spatial population density of the ground truth population"}
# adjustable break points for map categories
breaks <- c(0, 2, 5, 10, 20, 50, 100, 200, 350, Inf)
# plot map and print
area$area.sf %>% 
  mutate(pop.cat = cut(pop, breaks = breaks, dig.lab = 7, right = F)) %>% 
  map_density(data = ., var = "pop.cat", label = "GTP")

```

```{r pop-summary}
# summary descriptives of GTP
pop_summary_results(area$area.sf) %>% 
  dplyr::select(n.tiles = n.type, mean.pop, sd.pop, min.pop, max.pop, sum.pop)

```

```{r density-plot, fig.cap="ECCDF and ECDF of the ground truth population, (Insert ECDF capped at 30)"}
# ECCDF and ECDF of GTP
(density_plots(area$area.df))
```

## Toyworld Generation: Radio network

This subsection refers to the development of a radio network within our focus area. Developing the radio network is heavily dependent on the `mobloc` package, which is promoted through the European Statistical System. However, certain functions have been adjusted to the authors needs.

In general, the `mobloc` package allows to define many parameters, however, if they are not defined, default parameters, set by the package, are used. This makes it very easy to implement as much / as little information one has on a certain network and always making it work. The following adjustable parameters and default values are provided through the package for creating a radio network and modelling the signal strength in a focus area:

```{r}
# possible mobloc parameters
mobloc_param()
```

This toyworld contains a radio network with three layers (Macro, Meso and Micro). The development of each layer starts with a hexagonal grid in which the points define tower locations. The hexagons have different sizes (i.e. tower distance) dependent on the layer and contain some randomness within the layer (jitter) to prevent estimation artifacts. Each layer spans over the complete focus area.

On each tower three directional antennas are placed that are directed in a 120° angle to each other. All layers contain a rotation parameter to prevent antennas of different layers broadcasting into the exact same direction, in reference to the focus area. No omnidirectional antennas are implemented in this toyworld, therefore, all `mobloc` parameters with the suffix "\_small" are not used.

The antennas are specified with layer specific parameters (e.g. height, power, path loss exponent, etc.). All antennas are specified in a so called cellplan in which all parameters are nested/adjusted. When the cellplan is completed the antenna specific broadcasting profile (i.e. cell profile) is estimated and projected onto the focus area. The function `compute_sig_strength()` computes the distance, signal strength and signal dominance between any tile and any antenna. Furthermore, a minimum parameter is implemented that defines the minimum signal dominance value an antenna-tile relationship needs to have in order to be considered "covered". For the following estimators, it needs to be assured that every tile is sufficiently covered, meaning, that there is at least one antenna-tile relationship that has a signal dominance value higher than the minimum threshold.




```{r, network-parameters, message=FALSE, warning=FALSE, fig.height=8, fig.width=10, fig.cap="Theoretical radio network parameters for each layer"}
# specify parameters of each cell
ME.cell.param.mobloc <- mobloc_param(W = 50, range = 8000, ple = 3.7, height = 10,
                                     midpoint = -85, steepness = 0.3, sig_d_th = 0.05)

layer.list <- list(ME.cell.param.mobloc)

# create dataframe for theoretical signal strength distribution
param.df <- map_dfr(layer.list, rbind.data.frame) %>% 
  mutate(cell.kind = c("ME"),
         label = c("Meso")) %>% 
  dplyr::select(cell.kind, label, everything(), dominance.th = sig_d_th)

# reduced data frame of theoretical signal strength distribution
param.df.reduced <- param.df %>% 
  dplyr::select(cell.kind, dominance.th)

# theoretical signal strength parameter plots
sig.pram.plots <- sig_param_plots(param.df = param.df, range.max = 20000, base_size = 11)

# print
(a <- ggpubr::as_ggplot(sig.pram.plots$final))
# save
ggsave("Plots/coverage.diag.png", a, device = "png", width = 10)

set.seed(100)

layer.params.ext <- list(
  ME = list(tower.dist = 4000,
            rotation.deg = 35,
            jitter = 1,
            subscript = "ME",
            seed = 7,
            mobloc.params = ME.cell.param.mobloc)
  
)


cellplan.1.layer.1 <- complete_cellplan_gen(area = area,
                                            layer.params.ext = layer.params.ext,
                                            param.df = param.df)



# how many tiles are not sufficiently covered
paste0("Number of tiles which do not reach the signal dominance threshold of: " , sum(cellplan.1.layer.1$signal.dom$missing))

```


```{r, network-parameters, message=FALSE, warning=FALSE, fig.height=8, fig.width=10, fig.cap="Theoretical radio network parameters for each layer"}
# specify parameters of each cell
ME.cell.param.mobloc <- mobloc_param(W = 50, range = 8000, ple = 3.7, height = 10,
                                     midpoint = -85, steepness = 0.3, sig_d_th = 0.05)

layer.list <- list(ME.cell.param.mobloc)

# create dataframe for theoretical signal strength distribution
param.df <- map_dfr(layer.list, rbind.data.frame) %>% 
  mutate(cell.kind = c("ME"),
         label = c("Meso")) %>% 
  dplyr::select(cell.kind, label, everything(), dominance.th = sig_d_th)

# reduced data frame of theoretical signal strength distribution
param.df.reduced <- param.df %>% 
  dplyr::select(cell.kind, dominance.th)

# theoretical signal strength parameter plots
sig.pram.plots <- sig_param_plots(param.df = param.df, range.max = 20000, base_size = 11)

# print
(a <- ggpubr::as_ggplot(sig.pram.plots$final))
# save
ggsave("Plots/coverage.diag.png", a, device = "png", width = 10)

set.seed(100)

layer.params.ext <- list(
  ME = list(tower.dist = 3000,
            rotation.deg = 35,
            jitter = 1,
            subscript = "ME",
            seed = 7,
            mobloc.params = ME.cell.param.mobloc)
  
)


cellplan.1.layer.2 <- complete_cellplan_gen(area = area,
                                            layer.params.ext = layer.params.ext,
                                            param.df = param.df)



# how many tiles are not sufficiently covered
paste0("Number of tiles which do not reach the signal dominance threshold of: " , sum(cellplan.1.layer.2$signal.dom$missing))

```


```{r, network-parameters, message=FALSE, warning=FALSE, fig.height=8, fig.width=10, fig.cap="Theoretical radio network parameters for each layer"}
# specify parameters of each cell
MA.cell.param.mobloc <- mobloc_param(W = 5, # Power in Watts
                                     range = 10000, # maximum coverage range
                                     ple = 3.4, # Path loss exponent
                                     height = 10, # height of the antenna
                                     midpoint = -85, # midpoint parameter of the logistic function for signal dominance
                                     steepness = 0.15, # steepness parameter of the logistic function for signal dominance
                                     sig_d_th = 0.05) # dominance minimum threshold 

ME.cell.param.mobloc <- mobloc_param(W = 50, range = 3500, ple = 3.7, height = 10,
                                     midpoint = -85, steepness = 0.3, sig_d_th = 0.05)

MI.cell.param.mobloc <- mobloc_param(W = 1, range = 3500, ple = 4, height = 6,
                                     midpoint = -85, steepness = 0.4, sig_d_th = 0.05)

layer.list <- list(MA.cell.param.mobloc, ME.cell.param.mobloc, MI.cell.param.mobloc)

# create dataframe for theoretical signal strength distribution
param.df <- map_dfr(layer.list, rbind.data.frame) %>% 
  mutate(cell.kind = c("MA", "ME", "MI"),
         label = c("Macro", "Meso", "Micro")) %>% 
  dplyr::select(cell.kind, label, everything(), dominance.th = sig_d_th)

# reduced data frame of theoretical signal strength distribution
param.df.reduced <- param.df %>% 
  dplyr::select(cell.kind, dominance.th)

# theoretical signal strength parameter plots
sig.pram.plots <- sig_param_plots(param.df = param.df, range.max = 20000, base_size = 11)

# print
(a <- ggpubr::as_ggplot(sig.pram.plots$final))
# save
ggsave("Plots/coverage.diag.png", a, device = "png", width = 10)

set.seed(100)

layer.params.ext <- list(
  MA = list(tower.dist = 8500,
            rotation.deg = 0,
            jitter = 1000,
            subscript = "MA",
            seed = 3,
            mobloc.params = MA.cell.param.mobloc),
    ME = list(tower.dist = 3500,
            rotation.deg = 35,
            jitter = 700,
            subscript = "ME",
            seed = 7,
            mobloc.params = ME.cell.param.mobloc),
    MI = list(tower.dist = 10000,
            rotation.deg = 60,
            jitter = 2000,
            subscript = "MI",
            seed = 10,
            mobloc.params = MI.cell.param.mobloc)
  
)


cellplan.3.layer <- complete_cellplan_gen(area = area,
                                          layer.params.ext = layer.params.ext,
                                          param.df = param.df)



# how many tiles are not sufficiently covered
paste0("Number of tiles which do not reach the signal dominance threshold of: " , sum(cellplan.3.layer$signal.dom$missing))

```


```{r, network-parameters, message=FALSE, warning=FALSE, fig.height=8, fig.width=10, fig.cap="Theoretical radio network parameters for each layer"}
# specify parameters of each cell
ME.cell.param.mobloc <- mobloc_param(W = 50, range = 8000, ple = 3.7, height = 10,
                                     midpoint = -85, steepness = 0.3, sig_d_th = 0.05)

MI.cell.param.mobloc <- mobloc_param(W = 1, range = 3500, ple = 4, height = 6,
                                     midpoint = -85, steepness = 0.4, sig_d_th = 0.05)

layer.list <- list(ME.cell.param.mobloc, MI.cell.param.mobloc)

# create dataframe for theoretical signal strength distribution
param.df <- map_dfr(layer.list, rbind.data.frame) %>% 
  mutate(cell.kind = c("ME", "MI"),
         label = c("Meso", "Micro")) %>% 
  dplyr::select(cell.kind, label, everything(), dominance.th = sig_d_th)

# reduced data frame of theoretical signal strength distribution
param.df.reduced <- param.df %>% 
  dplyr::select(cell.kind, dominance.th)

# theoretical signal strength parameter plots
sig.pram.plots <- sig_param_plots(param.df = param.df, range.max = 20000, base_size = 11)

# print
(a <- ggpubr::as_ggplot(sig.pram.plots$final))
# save
ggsave("Plots/coverage.diag.png", a, device = "png", width = 10)

set.seed(100)

layer.params.ext <- list(
    ME = list(tower.dist = 4000,
            rotation.deg = 35,
            jitter = 700,
            subscript = "ME",
            seed = 7,
            mobloc.params = ME.cell.param.mobloc),
    MI = list(tower.dist = 10000,
            rotation.deg = 60,
            jitter = 2000,
            subscript = "MI",
            seed = 10,
            mobloc.params = MI.cell.param.mobloc)
  
)


cellplan.2.layer <- complete_cellplan_gen(area = area,
                                          layer.params.ext = layer.params.ext,
                                          param.df = param.df)



# how many tiles are not sufficiently covered
paste0("Number of tiles which do not reach the signal dominance threshold of: " , sum(cellplan.2.layer$signal.dom$missing))

```


```{r dev-to-cell}
# specify the option of differing parameters for sig_d_th and max_overlapping_cells depending on the cell type in custom create_strength_llh function

# Workaround: securing that sig_d_th and max_overlapping_cells are the same for each layer
signal.strength.llh.param <- list(sig_d_th = 0.05,
                                  max_overlapping_cells = 100)

# define connection llh and classify tiles depending on coverage status
connection.llh <- map(signal.strength.comb.dt, ~create_strength_llh_custom(.x,
                                                                           signal.strength.llh.param, 
                                                                           smart.rounding.digits = 3, 
                                                                           area.df = area$area.df))
                      

# create c-vector
C.vec.df <- map(connection.llh, ~create_c_vector(.x$signal.strength.llh.combined))

# develop long format of P matrix which also contains certain cellplan parameters and "zero elements"
# develop different versions of id variables (tile and antennas) for easier joining
P.long.complete.df <- map2(connection.llh, C.vec.df, ~full_join(.x$signal.strength.llh.combined, .y, by = "cell")) %>% 
  # dplyr::select(tile.id, pop, elevation, cell, type, dist, pij, phones.sum) %>% 
  map(~dplyr::select(., tile.id.chr,, tile.id.fac, tile.id.num, pop, cell, type, dist, pij, phones.sum)) %>% 
  map(~mutate(., cell.chr = as.character(cell))) %>% 
  map2(cellplan.combined, ~mutate(.x, cell.fac = factor(cell.chr, levels = fct_unique(.y$cell.fac)))) %>% 
  map(~mutate(., cell.num = as.numeric(cell.fac)))

# Long format of P matrix with minimal variables and and unique rows
P.long.df <- P.long.complete.df %>% 
  map(~dplyr::select(., tile.id.chr, tile.id.fac, tile.id.num, cell.chr, cell.fac, cell.num, pij)) %>% 
  map(~distinct(.))

```

