---
title: "Toyworld generation, Estimation and Evaluation"
author: "Marco Ramljak"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    code_folding: show
    code_download: true
    theme: sandstone
    toc: true
    toc_float: true
    number_sections: true
    fig_caption: yes
knit: (function(input_file, encoding) { out_dir <- 'docs'; rmarkdown::render(input_file,
  encoding=encoding, output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

This notebook shows the first version of the MNO analysis pipeline. The notebook has three main parts: Toyworld Generation, Estimation, Evaluation. The pipieline is constructed in a modular way and each part represents one module. This means that one can start and finish the pipeline to ones own liking at any starting or end point of a module. 

The toyworld is based on a semi-synthetic data generated process. For this, census data from Germany on a 100m\*100m regular grid has been used, which can be downloaded [here](https://www.zensus2011.de/DE/Home/Aktuelles/DemografischeGrunddaten.html?nn=3065474). Each element in this grid is expressed as a tile. For computation purposes only a small area of Germany was used for the toyworld, namely the area of Munich and its near surroundings. This focus area includes 160,000 tiles. For a mobile phone population the regular census population values are used. To mimic the mobile phone population of one mobile network operator (MNO) the population is reduced to about a third.

Furthermore, custom functions have been built and are used throughout this notebook. In near time, these will be released within an R-package.

# General Setup: Loading Packages and Custom Functions

```{r}
# Data manipulation
library(tidyverse)
library(data.table) 

# Spatial operations
library(sf)
library(raster)
library(furrr)
library(stars)

# Matrix operations
library(Matrix)

# MNO data handling and propagation model setup
# Credits to Prof. Martijn Tennekes https://github.com/mtennekes/mobloc
library(mobloc)

# Comparison of 2d histograms (Kantorovitch Wasserstein distance a.k.a. Earth Movers distance)
# Credits to Prof. Stefano Gualandi https://cran.r-project.org/web/packages/SpatialKWD/SpatialKWD.pdf
library(SpatialKWD)

# Output organisation and plotting support
library(ggthemes)
library(viridis)
library(ggrepel)
library(ggpointdensity)
library(scattermore)
library(grid)
library(gridExtra)
library(knitr)
library(DT)

# seed for reproducibility
set.seed(42)


# Loading Custom functions
source("pipeline functions.R")

```

# Toyworld Generation

This part is concerned with generating a toyworld that is based on the above specified focus area. After specifying the population aspect of the toyworld, the radio network will be specified. 

## Toyworld Generation: Population

This subchapter defines the generation of a population. As mentioned above the focus area is zoomed into the area of Munich and its near surroundings. It should be noted that an additional version of this subchapter is already created that gives options of creating a completely artificial focus area and population with multiple parameters to adjust. However, to present the complete functionality of the pipeline and its capability to also easily work with real data, the Munich area is chosen. The following chunk specifies the necessary objects to continue with the creation of a radio network in this focus area.

```{r population-data}
# data read in
munich.raw <- readRDS("Data/munich.rds")

# define raster object from focus area
munich.raster <- rasterFromXYZ(munich.raw, crs = st_crs(3035)$proj4string)

# define empty list object where all GTP objects will be stored
munich <- NULL

# define sf version of raster object
munich$area.sf <- munich.raster %>%
  st_as_stars() %>%
  st_as_sf() %>%
  mutate(centroid.geometry = st_centroid(.$geometry)) %>% 
  mutate(X.centroid = unlist(map(.$centroid.geometry, 1)),
         Y.centroid = unlist(map(.$centroid.geometry, 2))) %>% 
  dplyr::select(tile.id, pop, elevation, X.centroid, Y.centroid) %>%
  mutate(type = "NA") # only necessary if different tile types can be defined (urban, rural, etc...)

# regular dataframe version
munich$area.df <- munich$area.sf %>%
  st_drop_geometry()

# unionized version of focus area
munich$area.union <- munich$area.sf %>%
  st_union()

# bounding box coordinates of focus area
munich$area.bbox <- munich$area.union %>%
  st_bbox(crs = sf::st_crs(3035))

# specify raster object and tile id number
munich$area.raster <- munich.raster %>%
  raster(., layer = "tile.id")

# specify raster object and elevation value of each tile (here considered as constant)
munich$area.elevation <- munich.raster %>%
  raster(., layer = "elevation")

# number of tiles
munich$area.params[["tile.num"]] <- length(munich$area.df$tile.id)

# size of tiles
munich$area.params[["base.tile.size"]] <- as.numeric(sqrt(st_area(munich$area.sf[1,])))

# stroing everything in area object
area <- munich
```

```{r gtp-map, fig.cap="Spatial population density of the ground truth population"}
# adjustable break points for map categories
breaks <- c(0, 2, 5, 10, 20, 50, 100, 200, 350, Inf)
# plot map and print
area$area.sf %>% 
  mutate(pop.cat = cut(pop, breaks = breaks, dig.lab = 7, right = F)) %>% 
  map_density(data = ., var = "pop.cat", label = "GTP")

```


```{r pop-summary}
# summary descriptives of GTP
pop_summary_results(area$area.sf) %>% 
  dplyr::select(n.tiles = n.type, mean.pop, sd.pop, min.pop, max.pop, sum.pop)

```

```{r density-plot, fig.cap="Distribution of the ground truth population"}
# ECCDF and ECDF of GTP
(density_plots(area$area.df))
```

## Toyworld Generation: Radio network

This subchapter refers to the development of a radio network within our focus area. Developing the radio network is heavily dependent on the `mobloc` package, which is promoted through the European Statistical System. However, certain functions have been adjusted to the authors needs.

In general, the `mobloc` package allows to define many parameters, and, if they are not defined, default parameters, set by the package, are used. This makes it very easy to implement as much or as little information one has on a certain network and always making it work. The following adjustable parameters and default values are provided through the package for creating a radio network and modeling the signal strength in a focus area:

```{r}
# possible mobloc parameters
mobloc_param()
```

This toyworld contains a radio network with three layers (Macro, Meso and Micro). The development of each layer starts with a hexagonal grid in which the points define tower locations. The hexagons have different sizes (i.e. tower distance) dependent on the layer and contain some randomness within the layer (jitter) to prevent estimation artifacts. Each layer spans over the complete focus area.

On each tower three directional antennas are placed that are directed in a 120° angle to each other. All layers contain a rotation parameter to prevent antennas of different layers broadcasting into the exact same direction, in reference to the focus area. No omnidirectional antennas are implemented in this toyworld, therefore, all `mobloc` parameters with the suffix "\_small" are not used.

The antennas are specified with layer specific parameters (e.g. height, power, path loss exponent, etc.). All antennas are specified in a so called cellplan in which all parameters are nested/adjusted. When the cellplan is completed the antenna specific broadcasting profile (i.e. cell profile) is estimated and projected onto the focus area. The function `compute_sig_strength()` computes the distance, signal strength and signal dominance between any tile and any antenna. Furthermore, a minimum parameter is implemented that defines the minimum signal dominance value an antenna-tile relationship needs to have in order to be considered "covered". For the following estimators, it needs to be assured that every tile is sufficiently covered, meaning, that there is at least one antenna-tile relationship that has a signal dominance value higher than the minimum threshold. The signal dominance is a more interpretable measure for the signal strength and other aspects such as load balancing. This measure will be used later on to define the connection likelihood.

```{r, network-parameters, message=FALSE, warning=FALSE, fig.height=8, fig.width=10, fig.cap="Theoretical radio network parameters for each layer"}
# specify parameters of each cell
MA.cell.param.mobloc <- mobloc_param(W = 5, # Power in Watts
                                     range = 10000, # maximum coverage range
                                     ple = 3.4, # Path loss exponent
                                     height = 10, # height of the antenna
                                     midpoint = -85, # midpoint parameter of the logistic function for signal dominance
                                     steepness = 0.15, # steepness parameter of the logistic function for signal dominance
                                     sig_d_th = 0.05) # dominance minimum threshold 

ME.cell.param.mobloc <- mobloc_param(W = 50, range = 3500, ple = 3.8, height = 10,
                                     midpoint = -85, steepness = 0.3, sig_d_th = 0.05)

MI.cell.param.mobloc <- mobloc_param(W = 1, range = 3500, ple = 4, height = 6,
                                     midpoint = -85, steepness = 0.4, sig_d_th = 0.05)

# create dataframe for theoretical signal strength distribution
param.df <- tibble(cell.kind = c("MA", "ME", "MI"),
                   label = c("Macro", "Meso", "Micro"),
                   W = c(MA.cell.param.mobloc$W, ME.cell.param.mobloc$W, MI.cell.param.mobloc$W),
                   ple = c(MA.cell.param.mobloc$ple, ME.cell.param.mobloc$ple, MI.cell.param.mobloc$ple),
                   range = c(MA.cell.param.mobloc$range, ME.cell.param.mobloc$range, MI.cell.param.mobloc$range),
                   midpoint = c(MA.cell.param.mobloc$midpoint, ME.cell.param.mobloc$midpoint, MI.cell.param.mobloc$midpoint),
                   steepness = c(MA.cell.param.mobloc$steepness, ME.cell.param.mobloc$steepness, MI.cell.param.mobloc$steepness),
                   dominance.th = c(MA.cell.param.mobloc$sig_d_th,
                                    ME.cell.param.mobloc$sig_d_th,
                                    MI.cell.param.mobloc$sig_d_th))

# reduced data frame of theoretical signal strength distribution
param.df.reduced <- param.df %>% 
  dplyr::select(cell.kind, dominance.th)

# theoretical signal strength parameter plots
sig.pram.plots <- sig_param_plots(param.df = param.df, range.max = 20000, base_size = 11)

# print
(a <- ggpubr::as_ggplot(sig.pram.plots$final))
# save
ggsave("Plots/coverage.diag.png", a, device = "png", width = 10)

set.seed(100)

# create tower positions with attached cells
MA.cells.unparam <- create_cells(area.sf = area$area.sf, # focus area
                                 tower.dist = 8500, # tower distance
                                 rotation.deg = 0, # rotation parameter
                                 jitter = 1000, # amount of jitter in meters
                                 small = FALSE, # directional cell
                                 subscript = "MA", # layer label
                                 seed = 3)

ME.cells.unparam <- create_cells(area.sf = area$area.sf,
                                 tower.dist = 3500, rotation.deg = 35,
                                 jitter = 700, small = FALSE,
                                 subscript = "ME", seed = 7)

MI.cells.unparam <- create_cells(area.sf = area$area.sf,
                                 tower.dist = 10000, rotation.deg = 60,
                                 jitter = 2000, small = FALSE,
                                 subscript = "MI", seed = 10)


# create the cellplan and validate it with the specified parameters
MA.cellplan.val <- create_cellplan(area.sf = area$area.sf,  
                                   area.bbox = area$area.bbox, 
                                   area.elevation = area$area.elevation,
                                   cells.unparam = MA.cells.unparam,
                                   cell.param.mobloc = MA.cell.param.mobloc)

ME.cellplan.val <- create_cellplan(area.sf = area$area.sf,
                                   area.bbox = area$area.bbox,
                                   area.elevation = area$area.elevation,
                                   cells.unparam = ME.cells.unparam,
                                   cell.param.mobloc = ME.cell.param.mobloc)

MI.cellplan.val <- create_cellplan(area.sf = area$area.sf,
                                   area.bbox = area$area.bbox,
                                   area.elevation = area$area.elevation,
                                   cells.unparam = MI.cells.unparam,
                                   cell.param.mobloc = MI.cell.param.mobloc)
# cellplans need to be made valid!

cellplan.combined <- bind_rows(as_tibble(MA.cellplan.val$cellplan.val),
                               as_tibble(ME.cellplan.val$cellplan.val),
                               as_tibble(MI.cellplan.val$cellplan.val)) %>% 
  mutate(cell.kind = substr(cell, 1, 2)) %>% 
  left_join(param.df.reduced, by = "cell.kind") # join dominance threshold to use later in create_strength_llh()

# to join variable dominance.th later on
cellplan.combined.reduced <- cellplan.combined %>% 
  dplyr::select(cell, dominance.th)


# compute signal strength and device to cell association
MA.signal.strength <- compute_sig_strength(cp = MA.cellplan.val$cellplan.val, 
                                           raster = area$area.raster, 
                                           param = MA.cellplan.val$cell.param.mobloc, 
                                           elevation = area$area.elevation)

ME.signal.strength <- compute_sig_strength(cp = ME.cellplan.val$cellplan.val,
                                           raster = area$area.raster,
                                           param = ME.cellplan.val$cell.param.mobloc,
                                           elevation = area$area.elevation)

MI.signal.strength <- compute_sig_strength(cp = MI.cellplan.val$cellplan.val,
                                           raster = area$area.raster,
                                           param = MI.cellplan.val$cell.param.mobloc,
                                           elevation = area$area.elevation)

# create signal strength object of all cells
signal.strength.comb.dt <- rbindlist(list(MA.signal.strength,
                                          ME.signal.strength,
                                          MI.signal.strength))

  


signal.strength.summary.helper <- signal.strength.comb.dt %>%
  as_tibble() %>%
  mutate(tile.id = as.character(rid)) %>%
  mutate(cell.kind = substr(cell, 1, 2)) %>%
  mutate(cell.chr = as.character(cell)) %>%
  left_join(cellplan.combined.reduced, by = c("cell.chr" = "cell")) %>% 
  filter(!s < dominance.th) # filter rows out that are below the set dominance threshold

signal.strength.summary <- signal.strength.summary.helper %>% 
  group_by(tile.id) %>%
  mutate(max.dBm = max(dBm),
         max.s = max(s),
         min.dist = min(dist)) %>%
  ungroup()


# identify the cell-tile relations with maximum signal dominance and identify tiles that are not covered sufficiently
signal.dom <- signal.strength.summary %>% 
  distinct(tile.id, max.s) %>%
  left_join(signal.strength.summary, by = c("tile.id", "max.s" = "s")) %>% 
  dplyr::select(tile.id, max.s, cell, cell.kind) %>% 
  mutate(tile.id = as.integer(tile.id)) %>% 
  full_join(area$area.sf, by = "tile.id") %>% 
  mutate(missing = case_when(is.na(max.s) ~ 1,
                             TRUE ~ 0))

# how many tiles are not sufficiently covered
paste0("Number of tiles which do not reach the signal dominance threshold of: " , sum(signal.dom$missing))
# paste0("Number of tiles which do not reach the signal dominance threshold of ", sig_d_th, ": " , sum(signal.dom$missing))
```

The following chunk is merely executed to develop a smoother visualization of the radio cell coverage profiles. For this, the signal strength is calculated on a finer grid 25m\*25m. This finer grid is only relevant for this chunk and the following contour visualizations. The contours are interpolated based on the tiles' signal dominance values and the tile centroids.

```{r contur-plot-setup, message=FALSE}
# specifiy how much finer the grid should be
finer.grid.factor <- 2
finer.grid.tile.id <- c(1:640000) # adjust to grid factor

# disaggregate the regular grid based on the finer.grid.factor
area$area.raster.finer <- disaggregate(area$area.raster, finer.grid.factor) %>% 
  setValues(., finer.grid.tile.id)

# disaggregate the elevation grid based on the finer.grid.factor
area$area.elevation.finer <- disaggregate(area$area.elevation, finer.grid.factor)

# transform raster back to sf
area$area.finer.grid.sf <- st_as_sf(st_as_stars(area$area.raster.finer))

# compute signal strength and device to cell association for finer grid for each layer
MA.signal.strength.finer <- compute_sig_strength(cp = MA.cellplan.val$cellplan.val, 
                                                 raster = area$area.raster.finer, 
                                                 param = MA.cellplan.val$cell.param.mobloc, 
                                                 elevation = area$area.elevation.finer)

ME.signal.strength.finer <- compute_sig_strength(cp = ME.cellplan.val$cellplan.val,
                                                 raster = area$area.raster.finer,
                                                 param = ME.cellplan.val$cell.param.mobloc,
                                                 elevation = area$area.elevation.finer)

MI.signal.strength.finer <- compute_sig_strength(cp = MI.cellplan.val$cellplan.val,
                                                 raster = area$area.raster.finer,
                                                 param = MI.cellplan.val$cell.param.mobloc,
                                                 elevation = area$area.elevation.finer)

signal.strength.comb.dt.finer.grid <- rbindlist(list(MA.signal.strength.finer,
                                                     ME.signal.strength.finer,
                                                     MI.signal.strength.finer))


# calculate tile centroid for each tile on the finer grid
area.reduced.contour <- area$area.finer.grid.sf %>% 
  dplyr::select(tile.id.num = tile.id) %>% 
  st_centroid() %>% 
  mutate(lon = unlist(map(.$geometry, 1)),
         lat = unlist(map(.$geometry, 2)))

# set the coordinate reference system
crs.set <- st_crs(area.reduced.contour)

# compute the antenna specfic broadcasting profile contour
# define two categories: contour of signal dominance values below or equal to 0.5 and above 0.5 resulting later in two contour lines per antenna
contour.data.raw <- signal.strength.comb.dt.finer.grid %>%
  as_tibble() %>%
  mutate(tile.id.num = as.numeric(rid)) %>%
  mutate(cell.chr = as.character(cell)) %>%
  left_join(cellplan.combined, by = c("cell.chr" = "cell")) %>% 
  filter(!s < dominance.th) %>% 
  mutate(s.discrete = case_when(s <= 0.5 ~ 1,
                                s > 0.5 ~ 2)) %>% # define categoristation of contours
  dplyr::select(cell, cell.kind, x.tow = x, y.tow = y, direction, tile.id.num, s, s.discrete) %>% 
  left_join(area.reduced.contour, by = c("tile.id.num")) %>% 
  st_as_sf(coords = c("lon", "lat"), crs = crs.set) 

# split according to layer
contour.data.raw.split <- contour.data.raw %>% 
  st_drop_geometry() %>% 
  split(.$cell.kind) %>% 
  map(~distinct(., cell, x.tow, y.tow))

# summarise antenna specific contour as polygon and then compute the convex hull to result in simple contour line
contour.data.summary <- contour.data.raw %>% 
  dplyr::select(cell, cell.kind, s.discrete, s) %>% 
  dplyr::group_by(cell, cell.kind, s.discrete) %>%
  dplyr::summarise() %>%
  st_convex_hull()
```

```{r contour-MA, fig.cap="Coverage Contour of Macro cells, showing the area with less or equal than 0.5 signal dominance"}
(contour.complete.MA <- contour.data.summary %>% 
  filter(cell.kind == "MA" & s.discrete == "1") %>% 
  ggplot() +
  geom_sf(data = area$area.union) +
  geom_sf(color = "red", fill = "transparent") +
  geom_point(data = contour.data.raw.split$MA, aes(x = x.tow, y = y.tow), color = "black", shape = 2) +
  theme_minimal() +
  labs(x = "", y = ""))
ggsave("Plots/contour.complete.MA.finer.png", contour.complete.MA, device = "png")
```

```{r contour-ME, fig.cap="Coverage Contour of Meso cells, showing the area with less or equal than 0.5 signal dominance"}
(contour.complete.ME <- contour.data.summary %>% 
  filter(cell.kind == "ME" & s.discrete == "1") %>% 
  ggplot() +
  geom_sf(data = area$area.union) +
  geom_sf(color = "red", fill = "transparent") +
  geom_point(data = contour.data.raw.split$ME, aes(x = x.tow, y = y.tow), color = "blue", shape = 2) +
  theme_minimal() +
  labs(x = "", y = ""))
ggsave("Plots/contour.complete.ME.finer.png", contour.complete.ME, device = "png")

```

```{r contour-MI, fig.cap="Coverage Contour of Micro cells, showing the area with less or equal than 0.5 signal dominance"}
(contour.complete.MI <- contour.data.summary %>% 
  filter(cell.kind == "MI" & s.discrete == "1") %>% 
  ggplot() +
  geom_sf(data = area$area.union) +
  geom_sf(color = "red", fill = "transparent") +
  geom_point(data = contour.data.raw.split$MI, aes(x = x.tow, y = y.tow), color = "green", shape = 2) +
  theme_minimal() +
  labs(x = "", y = ""))
ggsave("Plots/contour.complete.MI.finer.png", contour.complete.MI, device = "png")
```

```{r contour-certain, fig.cap="Coverage Contour of a sample cell of each layer, showing the discretized signal dominance (cell profile)"}

(contour.certain <- contour.data.summary %>% 
  filter(str_detect(cell, "MA.12.|ME.100.|MI.18.")) %>% 
  ggplot() +
  geom_sf(data = area$area.union) +
  geom_sf(aes(color = factor(s.discrete)), fill = "transparent") +
  geom_point(data = contour.data.raw.split$MA, aes(x = x.tow, y = y.tow), color = "black", shape = 2) +
  geom_point(data = contour.data.raw.split$ME, aes(x = x.tow, y = y.tow), color = "blue", shape = 2) +
  geom_point(data = contour.data.raw.split$MI, aes(x = x.tow, y = y.tow), color = "green", shape = 2) +
  scale_color_discrete("Signal dom.", breaks = c("1", "2"), labels = c("0.05 <= s < 0.5",
                                                                      "s >= 0.5")) +
  theme_minimal() +
  labs(x = "", y = ""))
ggsave("Plots/hull.certain.finer.png", contour.certain, device = "png")

```

The following chunks visualizes different views on antenna coverage, specific for each layer.

```{r coverage-kind-setup}
# maximum of two rows per tile, tiles with only one row, mean they are only covered by one cell.kind
signal.strength.summary.ck <- signal.strength.summary.helper %>% 
  group_by(tile.id, cell.kind) %>%
  summarise(cell.count = n(),
            max.dBm = max(dBm),
            max.s = max(s),
            min.dist = min(dist)) %>% 
  mutate(cell.count.complete = sum(cell.count),
         max.dBm.complete = max(max.dBm),
         max.s.complete = max(max.s), 
         min.dist.complete = max(min.dist)) %>% 
  ungroup() %>% 
  pivot_longer(cols = -c(tile.id, cell.kind),
               names_to = "kind", 
               values_to = "values") # possibly different pivot to get "kind" into multiple variables
```

```{r histogram-cells, fig.cap="The number of cells a tile is covered by, in total and per cell layer"}
# histogram cells
(tile.coverage.hist <- signal.strength.summary.ck %>%
  filter(str_detect(kind, pattern = "count")) %>% 
  mutate(cat = case_when(str_detect(kind, pattern = "complete") ~ "complete",
                         TRUE ~ paste0(cell.kind))) %>% 
  distinct(tile.id, cat, .keep_all = T) %>% 
  dplyr::select(-cell.kind) %>% 
  ggplot() +
  geom_histogram(aes(values), binwidth = 1) +
  # scale_x_continuous(breaks = seq(0, 12, 1)) + # respecify to be dynamic
  facet_grid(~cat) +
  labs(title = "Number of cells a tile is covered by",
       y = "Tile count",
       x = "Number of cells"))
```

```{r coverage-map-dfs}
coverage.map.dom.df.MA <- signal.strength.summary.ck %>%
  filter(str_detect(kind, pattern = "max.s")) %>% 
  mutate(cat = case_when(str_detect(kind, pattern = "complete") ~ "complete",
                         TRUE ~ paste0(cell.kind))) %>% 
  filter(cat == "MA") %>% 
  dplyr::select(-cell.kind) %>% 
  mutate(tile.id.num = as.numeric(tile.id)) %>% 
  full_join(area$area.sf, by = c("tile.id.num" = "tile.id")) %>%  # change later on
  mutate(missing = case_when(is.na(values) ~ 1,
                             TRUE ~ 0)) %>% 
  st_as_sf()

coverage.map.dom.df.ME <- signal.strength.summary.ck %>%
  filter(str_detect(kind, pattern = "max.s")) %>% 
  mutate(cat = case_when(str_detect(kind, pattern = "complete") ~ "complete",
                         TRUE ~ paste0(cell.kind))) %>% 
  filter(cat == "ME") %>% 
  dplyr::select(-cell.kind) %>% 
  mutate(tile.id.num = as.numeric(tile.id)) %>% 
  full_join(area$area.sf, by = c("tile.id.num" = "tile.id")) %>%  # change later on
  mutate(missing = case_when(is.na(values) ~ 1,
                             TRUE ~ 0)) %>% 
  st_as_sf()

coverage.map.dom.df.MI <- signal.strength.summary.ck %>%
  filter(str_detect(kind, pattern = "max.s")) %>% 
  mutate(cat = case_when(str_detect(kind, pattern = "complete") ~ "complete",
                         TRUE ~ paste0(cell.kind))) %>% 
  filter(cat == "MI") %>% 
  dplyr::select(-cell.kind) %>% 
  mutate(tile.id.num = as.numeric(tile.id)) %>% 
  full_join(area$area.sf, by = c("tile.id.num" = "tile.id")) %>%  # change later on
  mutate(missing = case_when(is.na(values) ~ 1,
                             TRUE ~ 0)) %>% 
  st_as_sf()

coverage.map.dom.df.complete <- signal.strength.summary.ck %>%
  filter(str_detect(kind, pattern = "max.s")) %>% 
  mutate(cat = case_when(str_detect(kind, pattern = "complete") ~ "complete",
                         TRUE ~ paste0(cell.kind))) %>% 
  filter(cat == "complete") %>% 
  distinct(tile.id, cat, .keep_all = T) %>% 
  dplyr::select(-cell.kind) %>% 
  mutate(tile.id.num = as.numeric(tile.id)) %>% 
  full_join(area$area.sf, by = c("tile.id.num" = "tile.id")) %>%  # change later on
  mutate(missing = case_when(is.na(values) ~ 1,
                             TRUE ~ 0)) %>% 
  st_as_sf()
```

```{r coverage-map-MA, fig.cap="Actual coverage heatmap for Macro cells"}

system.time({
  coverage.map.MA <- coverage.map.dom.df.MA %>% 
    ggplot() +
    geom_sf(aes(fill = values), color = "transparent") +
    geom_point(data = as_tibble(MA.cellplan.val$cellplan.val), aes(x, y),
               shape = 2, color = "#F8766D") +
    scale_fill_gradient(low = "white", high = "black", na.value = "red", 
                        limits = c(0, 1)) +
    labs(title = "MA Coverage", 
         fill = "Signal Dominance",
         x = "",
         y = "") +
    theme_minimal() +
    theme(plot.margin = unit(c(0, 0, 0, 0), "cm"),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          legend.position = "none")
  print(coverage.map.MA)
})

```

```{r coverage-map-ME, fig.cap="Actual coverage heatmap for Meso cells"}
(coverage.map.ME <- coverage.map.dom.df.ME %>% 
    ggplot() +
    geom_sf(aes(fill = values), color = "transparent") +
    geom_point(data = as_tibble(ME.cellplan.val$cellplan.val), aes(x, y),
               shape = 2, color = "#00BFC4") +
    scale_fill_gradient(low = "white", high = "black", na.value = "red", 
                        limits = c(0, 1)) +
    labs(title = " ME Coverage", 
         fill = "Signal Dominance",
         x = "",
         y = "") +
    theme_minimal() +
    theme(plot.margin = unit(c(0, 0, 0, 0), "cm"),
          legend.position = "none",
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank()))


```

```{r coverage-map-MI, fig.cap="Actual coverage heatmap for Micro cells"}
(coverage.map.MI <- coverage.map.dom.df.MI %>% 
    ggplot() +
    geom_sf(aes(fill = values), color = "transparent") +
    geom_point(data = as_tibble(MI.cellplan.val$cellplan.val), aes(x, y),
               shape = 2, color = "#00BFC4") +
    scale_fill_gradient(low = "white", high = "black", na.value = "red", 
                        limits = c(0, 1)) +
    labs(title = " MI Coverage", 
         fill = "Signal Dominance",
         x = "",
         y = "") +
    theme_minimal() +
    theme(plot.margin = unit(c(0, 0, 0, 0), "cm"),
          legend.position = "none",
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank()))
```

```{r coverage-map-complete, fig.cap="Actual coverage heatmap for all cells"}

(coverage.map.complete <- coverage.map.dom.df.complete %>% 
    ggplot() +
    geom_sf(aes(fill = values), color = "transparent") +
    geom_point(data = cellplan.combined, aes(x, y, color = cell.kind),
               shape = 2) +
    scale_fill_gradient(low = "white", high = "black", na.value = "red", 
                        limits = c(0, 1)) +
    labs(title = "Complete coverage", 
         color = "Tower kind",
         fill = "Signal Dominance",
         x = "",
         y = "") +
    theme_minimal() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank()))
```

```{r coverage-multinomial-setup}
coverage.map.dom.df.binary <- signal.strength.summary.ck %>%
  filter(str_detect(kind, pattern = "max.s"),
         !str_detect(kind, pattern = "complete")) %>%
  group_by(tile.id) %>%
  # mutate(values = round(values, 2)) %>%
  filter(values == max(values)) %>%
  ungroup() %>%
  mutate(tile.id.num = as.numeric(tile.id)) %>%
  full_join(area$area.sf, by = c("tile.id.num" = "tile.id")) %>%  # change later on
  mutate(missing = case_when(is.na(values) ~ 1,
                             TRUE ~ 0)) %>%
  st_as_sf()
```

```{r coverage-multinomial-map, fig.cap=""}
(coverage.map.binary <- coverage.map.dom.df.binary %>%
    ggplot() +
    geom_sf(aes(fill = cell.kind), color = "transparent", alpha = 0.3, show = FALSE) +
    geom_point(data = cellplan.combined, aes(x, y, color = cell.kind),
               shape = 2) +
    labs(title = "Maximum coverage categorized by cell layer",
         color = "Cell kind",
         x = "",
         y = "") +
    theme_minimal() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank()))
```

## Toyworld Generation: Device to cell association

This subchapter refers to the final task in the toyworld generation: the device to cell association. Here we bring the population with the network together and stochastically assign the mobile phone population in each tile to the respective antennas. The result is the so-called c-vector, which describes the number of mobile phones assigned to each cell. The c-vector represents the "observation" an MNO provider collects at a specific point of time. The basis parameter for this assignment is the signal dominance which is normalized in the form of a conditional probability. These conditional probabilities describe the elements of the P.matrix, which is the main model to estimate (geolocation module).

```{r dev-to-cell}
# specify the option of differing parameters for sig_d_th and max_overlapping_cells depending on the cell type in custom create_strength_llh function

# Workaround: securing that sig_d_th and max_overlapping_cells are the same for each layer
signal.strength.llh.param <- list(sig_d_th = max(cellplan.combined.reduced$dominance.th),
                                  max_overlapping_cells = 100)

# defining the connection probability
signal.strength.llh.combined <- create_strength_llh(strength = signal.strength.comb.dt, 
                                                    param = signal.strength.llh.param) %>% 
  as_tibble() %>% 
  mutate(tile.id = rid) %>% 
  group_by(tile.id) %>%
  mutate(pij = smart_round(pag, 3)) %>% # round values to the third decimal and assuring that all columns (tiles) add up to 1 (column stocahsticity)
  ungroup() %>%
  left_join(area$area.df, by = "tile.id") %>% 
  mutate(coverage.kind = case_when(pop == 0 ~ "0 population",
                                   pij == 1 ~ "covered completely by one antenna",
                                   pij > 0 & pij < 1 ~ "covered by multiple antennas",
                                   pij == 0 ~ "tile covered unsufficiently")) %>% 
  dplyr::select(-pag)

# aggregating and specifying the tiles that are uncovered (if there are some)
tiles.cat <- signal.strength.llh.combined %>% 
  filter(!pij == 0) %>% 
  dplyr::select(tile.id, coverage.kind) %>% 
  group_by(tile.id) %>% 
  summarise(count = n())

# how many tiles are not sufficiently covered
missings <- anti_join(area$area.df, tiles.cat, by = "tile.id") # implement non zero pop
paste("Number of tiles which are unsufficiently covered:", length(missings$tile.id))

# covered only by one tile
C.vec.fixed.helper <- signal.strength.llh.combined %>% 
  filter(coverage.kind == "covered completely by one antenna") %>%
  dplyr::select(tile.id, cell, pop)

# One object where tiles are covered by multiple cells
C.vec.multiple.helper.new <- signal.strength.llh.combined %>% 
  filter(coverage.kind == "covered by multiple antennas") %>% 
  split(.$tile.id) 

# Sampling mobile phones within tiles to cells depending on connection probability
C.vec.multiple <- C.vec.multiple.helper.new %>% 
  map(c.vec.sampler) %>% 
  map(setattr, name = "class", value = "data.table") %>% 
  rbindlist(.) %>% 
  .[, .N, by = V1] %>% 
  as_tibble() %>% 
  dplyr::select(cell = V1, pop = N)

# pulling all c-vec helper objects together and develop final c-vec dataframe
C.vec.df <- C.vec.multiple %>% 
  bind_rows(C.vec.fixed.helper) %>%
  group_by(cell) %>% 
  summarise(phones.sum = sum(pop))
```

```{r c-vec-distribution, fig.cap="Distribution of the toyworld population"}
# log scale breaks for background grid
minor.breaks <- rep(1:9, 21) * (10^rep(-10:10, each = 9))

# develop c-vec dataset for plotting eccdf and ecdf
c.vec.density.data <- C.vec.df %>% 
    mutate(c.plot = phones.sum + 1) %>%  
    arrange(c.plot) %>%  
    mutate(prob = 1 / n()) %>%  
    mutate(cum.prob = cumsum(prob)) %>%  
    mutate(cum.prob.comp = 1 - cum.prob) %>%  
    dplyr::select(cum.prob.comp, c.plot) 

# ECCDF plot c-vec
c.vec.eccdf <- c.vec.density.data %>% 
    ggplot() +
    geom_point(aes(x = c.plot, y = cum.prob.comp)) +
    scale_y_log10(labels = scales::trans_format("log10", 
                                                scales::math_format(10^.x)),
                  minor_breaks = minor.breaks) +
    scale_x_log10(labels = scales::trans_format("log10", 
                                                scales::math_format(10^.x)),
                  minor_breaks = minor.breaks) +
    annotation_logticks(sides = "lb") +
    labs(title = "Number of phones a cell has registered (ECCDF and ECDF)",
         y = "log(ECCDF)",
         x = "Number of phones")

# ECDF plot c-vec
c.vec.ecdf <- c.vec.density.data %>%   
  ggplot() + 
  geom_point(aes(x = c.plot, y = cum.prob.comp)) + 
  labs(title = "", y = "", x = "") +
  theme(legend.position = "none",
        plot.margin = unit(c(-0.5, 0, 0, -0.5), "cm")) 


(combined.c.vec <- c.vec.eccdf +
  annotation_custom(ggplotGrob(c.vec.ecdf), 
                    xmin = 0.2, xmax = 3, 
                    ymin = -2.8, ymax = -1))
ggsave("Plots/histogram.c.vec.png", combined.c.vec, device = "png")
```

In the following code chunk we are specifying the P matrix, with tiles as columns, antennas as rows and antenna-tile relationships as the elements. This matrix can be described as the connection probability. Each column adds up to 1, meaning it is column stochastic. This particular version of the connection probability can be described as exact, as it represents the same information which is used for the data generating mechanism in the development of the toyworld. We will define a copy of the P matrix, which will be called P\* (P.star) and describes the modeling parameter necessary for all estimators, excluding the Voronoi estimators. For the sensitivity analysis different versions of this P.matrix will be defined and used for the estimators. Each version will represent a different level of certainty on the network coverage. Through this sensitivity analysis, we will be able to scrutinize the effect of different levels of (valid) information available. A practical question is: If one were to know only little about the network coverage profile of a specific area, how accurate will the final estimations on the tile level still be? 

Furthermore, in the following code chunk we implement the process of consolidation a.k.a. the development of super tiles. These are tiles in the P matrix that are indistinguishable from each other based on their relationships to antennas (i.e. columns in the P matrix that are exactly the same). These tiles will yield in all estimators the exact same value, therefore, to reduce computational resources, they can be consolidated to supertiles and afterwards disaggregated again.


```{r}
P.long.complete.df <- full_join(signal.strength.llh.combined, C.vec.df, by = "cell") %>% 
  # dplyr::select(tile.id, pop, elevation, cell, type, dist, pij, phones.sum) %>% 
  dplyr::select(tile.id, pop, cell, type, dist, pij, phones.sum) %>% 
  mutate(tile.id.chr = tile.id) %>% 
  mutate(tile.id = factor(tile.id)) %>% 
  mutate(tile.id.num = as.numeric(tile.id)) %>% 
  mutate(cell.num = as.numeric(cell)) %>% 
  mutate(cell.chr = as.character(cell))

P.long.df <- P.long.complete.df %>% 
  dplyr::select(tile.id, tile.id.num, tile.id.chr, cell, cell.num, cell.chr, pij) %>% 
  distinct()


P.mat <- sparseMatrix(i = P.long.df$cell.num, 
                      j = P.long.df$tile.id.num, 
                      x = P.long.df$pij)


########### Super tiles with oracle
P.star.supertile.helper <- P.long.df %>% 
  dplyr::select(tile.id.chr, cell.chr, pij) %>% 
  filter(!pij == 0) %>%
  group_by(tile.id.chr) %>% 
  arrange(cell.chr) %>% 
  mutate(cell.comp = paste0(cell.chr, collapse = ""),
         pij.comp = paste0(pij, collapse = "")) %>% 
  ungroup() %>% 
  group_by(cell.comp, pij.comp) %>% 
  mutate(supertile.id = cur_group_id()) %>% 
  ungroup() %>% 
  mutate(supertile.id = factor(supertile.id)) %>% 
  mutate(supertile.id.num = as.numeric(supertile.id)) %>% 
  mutate(supertile.id.chr = as.character(supertile.id)) %>% 
  right_join(P.long.df, by = c("tile.id.chr", "cell.chr")) %>% 
  dplyr::select(tile.id, tile.id.num, tile.id.chr, supertile.id, supertile.id.num, supertile.id.chr, 
                cell, cell.num, cell.chr, pij = pij.x) %>% 
  filter(!is.na(pij)) # check this

P.star.supertile.joiner <- P.star.supertile.helper %>%  
  distinct(tile.id.num, supertile.id, supertile.id.num, supertile.id.chr) %>% 
  arrange(tile.id.num) 

  
P.star.supertile.helper %>%  
  distinct(tile.id, tile.id.num, tile.id.chr, supertile.id, supertile.id.num, supertile.id.chr, .keep_all = T) %>% 
  group_by(supertile.id.num) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  group_by(n) %>% 
  summarise(count = n()) %>% 
  datatable(caption = "Distribution of supertiles", rownames = F)


P.star.supertile.long.df <- P.star.supertile.helper %>%
  distinct(supertile.id, supertile.id.num, supertile.id.chr, cell, cell.num, cell.chr, pij) %>% 
  arrange(cell.num)


########### Super tiles with equal
P.star.long.df <- P_equalizer(P.long.df, signal.strength.comb.dt)

P.star.equal.supertile.helper <- P.star.long.df %>% 
  dplyr::select(tile.id.chr, cell.chr, pij.equal) %>% 
  filter(!pij.equal == 0) %>%
  group_by(tile.id.chr) %>% 
  arrange(cell.chr) %>% 
  mutate(cell.comp = paste0(cell.chr, collapse = ""),
         pij.equal.comp = paste0(pij.equal, collapse = "")) %>% 
  ungroup() %>% 
  group_by(cell.comp, pij.equal.comp) %>% 
  mutate(supertile.equal.id = cur_group_id()) %>% 
  ungroup() %>% 
  mutate(supertile.equal.id = factor(supertile.equal.id)) %>% 
  mutate(supertile.equal.id.num = as.numeric(supertile.equal.id)) %>% 
  mutate(supertile.equal.id.chr = as.character(supertile.equal.id)) %>% 
  right_join(P.star.long.df, by = c("tile.id.chr", "cell.chr")) %>% 
  dplyr::select(tile.id, tile.id.num, tile.id.chr, supertile.equal.id, supertile.equal.id.num, supertile.equal.id.chr, 
                cell, cell.num, cell.chr, pij.equal = pij.equal.x) %>% 
  filter(!is.na(pij.equal)) # check this

P.star.equal.supertile.joiner <- P.star.equal.supertile.helper %>%  
  distinct(tile.id.num, supertile.equal.id, supertile.equal.id.num, supertile.equal.id.chr) %>% 
  arrange(tile.id.num) 


P.star.equal.supertile.helper %>%  
  distinct(tile.id, tile.id.num, tile.id.chr, supertile.equal.id, supertile.equal.id.num, supertile.equal.id.chr, .keep_all = T) %>% 
  group_by(supertile.equal.id.num) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  group_by(n) %>% 
  summarise(count = n()) %>% 
  datatable(caption = "Distribution of supertiles equal", rownames = F)


P.star.equal.supertile.long.df <- P.star.equal.supertile.helper %>%
  distinct(supertile.equal.id, supertile.equal.id.num, supertile.equal.id.chr, cell, cell.num, cell.chr, pij.equal) %>% 
  arrange(cell.num)


# append supertile id (oracle and equal) to sim area base objects
area$area.sf.complete <- area$area.sf %>% 
  left_join(P.star.supertile.joiner, by = c("tile.id" = "tile.id.num")) %>% 
  left_join(P.star.equal.supertile.joiner, by = c("tile.id" = "tile.id.num")) 
area$area.df.complete <- area$area.df %>% 
  left_join(P.star.supertile.joiner, by = c("tile.id" = "tile.id.num")) %>% 
  left_join(P.star.equal.supertile.joiner, by = c("tile.id" = "tile.id.num")) 

```

# Modelling P via P* (one with oracle and one with equal probability)

```{r}

#### P* oracle
P.star.oracle.dt.d <- P.long.df %>% 
  dplyr::select(i = cell.num, j = tile.id.num, pij) %>% 
  as.data.table()

P.star.oracle.supertile.spm <- sparseMatrix(i = P.star.supertile.long.df$cell.num, 
                                            j = P.star.supertile.long.df$supertile.id.num, 
                                            x = P.star.supertile.long.df$pij)

P.star.oracle.supertile.dt <- data.table(i = P.star.supertile.long.df$cell.num,
                                         j = P.star.supertile.long.df$supertile.id.num,
                                         pij = P.star.supertile.long.df$pij)



#### P* equal
P.star.equal.dt <- P.star.long.df %>% 
  dplyr::select(i = cell.num, j = tile.id.num, pij = pij.equal) %>% 
  as.data.table()

P.star.equal.supertile.spm <- sparseMatrix(i = P.star.equal.supertile.long.df$cell.num, 
                                            j = P.star.equal.supertile.long.df$supertile.equal.id.num, 
                                            x = P.star.equal.supertile.long.df$pij.equal)

P.star.equal.supertile.dt <- data.table(i = P.star.equal.supertile.long.df$cell.num,
                                         j = P.star.equal.supertile.long.df$supertile.equal.id.num,
                                         pij = P.star.equal.supertile.long.df$pij.equal)


# P.new <- P.long.df %>% 
#   mutate(pij.new = 1) %>% # same prob for all non-zero relationships
#   group_by(tile.id.num) %>% 
#   mutate(pij.new = pij.new / sum(pij.new)) %>%
#   ungroup() %>% 
#   as.data.table()
# 
# d <- P.new %>% 
#   filter(str_detect(cell, "MA.12.")) %>% 
#   left_join(area$area.sf, by = c("tile.id.chr")) %>% 
#   mutate(tile.id.chr = as.character(tile.id.chr)) %>% 
#   left_join(signal.strength.summary.helper, by = c("cell", "tile.id.chr" = "tile.id")) %>% 
#   st_sf()
# 
# s.plot <- d %>% 
#   # group_by(tile.id.chr) %>% 
#   # mutate(f = max())  %>% 
#   ggplot() +
#   geom_sf(aes(fill = s), color = "transparent") +
#   facet_wrap(vars(cell)) +
#   labs(title = "signal dominance") +
#   theme(axis.text = element_text(size = 4))
# 
# oracle.plot <- d %>% 
#   ggplot() +
#   geom_sf(aes(fill = pij), color = "transparent") +
#   facet_wrap(vars(cell))+
#   labs(title = "oracle") +
#   theme(axis.text = element_text(size = 4))
# 
# 
# equal.plot <- d %>% 
#   ggplot() +
#   geom_sf(aes(fill = pij.new), color = "transparent") +
#   facet_wrap(vars(cell))+
#   labs(title = "equal") +
#   theme(axis.text = element_text(size = 4))
# 
# coverage.example <- arrangeGrob(s.plot, oracle.plot, equal.plot,
#                                 layout_matrix = rbind(c(1),
#                                                       c(2),
#                                                       c(3)))
# 
# ggsave("coverage.example.png", coverage.example, device = "png")
# 


```


# Prepare objects necessary for estimation

```{r}
### C vector, adding antennas that have 0 phones to complete the vector, arranging it according to the antenna.ID and saving as vector
c.vec <- P.long.complete.df %>% 
  distinct(cell, cell.num, cell.chr, phones.sum) %>% 
  right_join(cellplan.combined, by = "cell") %>% 
  mutate(phones.sum = case_when(is.na(phones.sum) ~ 0,
                                TRUE ~ phones.sum)) %>% 
  arrange(cell.num)

c.vec.dt <- data.table(i = c.vec$cell.num,
                       c = c.vec$phones.sum)


### prior vectors
a.tile.helper <- P.long.complete.df %>% 
  mutate(a = 1) %>% 
  distinct(tile.id.num, a)
a.tile.dt <- data.table(j = a.tile.helper$tile.id.num, u = a.tile.helper$a)

a.supertile.helper <- P.star.supertile.joiner %>% 
  group_by(supertile.id.num) %>% 
  summarise(a = n()) %>% 
  ungroup() %>% 
  distinct(supertile.id.num, a) %>% 
  deframe()

a.equal.supertile.helper <- P.star.equal.supertile.joiner %>% 
  group_by(supertile.equal.id.num) %>% 
  summarise(a = n()) %>% 
  ungroup() %>% 
  distinct(supertile.equal.id.num, a) %>% 
  deframe()
```

```{r}
# Voronoi

# Voronoi estimation with tower locations as seeds
VOR.tower <- VOR_est(area = area, 
                     cellplan.combined = cellplan.combined, 
                     signal.strength.comb.dt = signal.strength.comb.dt, 
                     C.vec.df = C.vec.df, 
                     seed = "tower")
VOR.tower.est <- VOR.tower$seed.voronoi.final %>% 
  rename(u.VOR.tower = u.VOR)


# Voronoi estimation with cell locations + offset as seeds
VOR.offset <- VOR_est(area = area, 
                     cellplan.combined = cellplan.combined, 
                     signal.strength.comb.dt = signal.strength.comb.dt, 
                     C.vec.df = C.vec.df, 
                     seed = "cell.offset",
                     offset = 10) 
VOR.offset.est <- VOR.offset$seed.voronoi.final %>% 
  rename(u.VOR.offset = u.VOR)


# Voronoi estimation with cell hotpoint locations as seeds
VOR.hotpoint <- VOR_est(area = area, 
                        cellplan.combined = cellplan.combined, 
                        signal.strength.comb.dt = signal.strength.comb.dt, 
                        C.vec.df = C.vec.df, 
                        seed = "cell.hotpoint") 
VOR.hotpoint.est <- VOR.hotpoint$seed.voronoi.final %>% 
  rename(u.VOR.hotpoint = u.VOR)

# Voronoi estimation with cell barycenter locations as seeds
VOR.barycenter <- VOR_est(area = area, 
                        cellplan.combined = cellplan.combined, 
                        signal.strength.comb.dt = signal.strength.comb.dt, 
                        C.vec.df = C.vec.df, 
                        seed = "cell.barycenter") 
VOR.barycenter.est <- VOR.barycenter$seed.voronoi.final %>% 
  rename(u.VOR.barycenter = u.VOR)

VOR.tower$Voronoi.regions.plot
ggsave("Voronoi/tower.png", VOR.tower$Voronoi.regions.plot, device = "png")
VOR.offset$Voronoi.regions.plot
ggsave("Voronoi/offset.png", VOR.offset$Voronoi.regions.plot, device = "png")
VOR.hotpoint$Voronoi.regions.plot
ggsave("Voronoi/hotpoint.png", VOR.hotpoint$Voronoi.regions.plot, device = "png")
VOR.barycenter$Voronoi.regions.plot
ggsave("Voronoi/barycenter.png", VOR.barycenter$Voronoi.regions.plot, device = "png")


```

# SB estimator
```{r}
SB.oracle.est <- EM_est(c.vec.dt = c.vec.dt, 
                        P.dt = P.star.oracle.dt.d, 
                        a.vec.dt = a.tile.dt, 
                        selected.range = 1,
                        n.iter = 1) %>% 
  dplyr::rename(tile.id = j, prior.SB.oracle = i.u, u.SB.oracle = u1)

SB.equal.est <- EM_est(c.vec.dt = c.vec.dt, 
                       P.dt = P.star.equal.dt, 
                       a.vec.dt = a.tile.dt, 
                        selected.range = 1,
                        n.iter = 1) %>% 
  dplyr::rename(tile.id = j, prior.SB.equal = i.u, u.SB.equal = u1)
```

# EM estimator, 200 iterations

```{r}
# EM equal probability
EM.equal.est <- EM_est(c.vec.dt = c.vec.dt, 
                       P.dt = P.star.equal.dt, 
                       a.vec.dt = a.tile.dt, 
                       selected.range = c(1:10, 20, 50, seq(100, 200, 50)),
                       n.iter = 200) %>% 
  rename_with(.fn = ~gsub("u", "u.EM.equal", x = .x, fixed = T), 
              .cols = starts_with("u")) %>% 
  rename(tile.id = j, prior.EM.equal = i.u)

# EM oracle 
EM.oracle.est <- EM_est(c.vec.dt = c.vec.dt, 
                        P.dt = P.star.oracle.dt.d, 
                        a.vec.dt = a.tile.dt, 
                        selected.range = c(1:10, seq(20, 90, 10), seq(100, 200, 50)),
                        n.iter = 200) %>% 
  rename_with(.fn = ~gsub("u", "u.EM.oracle", x = .x, fixed = T), 
              .cols = starts_with("u")) %>% 
  rename(tile.id = j, prior.EM.oracle = i.u)
```


# 1 DF estimator with EM iterations

```{r}
## DF oracle

DF.oracle.est <- DF_est(c.vec.dt = c.vec.dt, 
                        P.star.spm = P.star.oracle.supertile.spm, 
                        a.supertile.vec = a.supertile.helper)
DF.oracle.est.dt <- data.table(j = as.numeric(names(a.supertile.helper)),
                               u = DF.oracle.est) %>%
  .[, u := fifelse(u < 1, 1, u)] # set negative values immediately to 0

## Renormalizing with EM and bringing estimate on tile.id level
DF_EM.oracle.est <- EM_est(c.vec.dt = c.vec.dt, 
                           P.dt = P.star.oracle.supertile.dt, a.vec.dt = DF.oracle.est.dt,
                           selected.range = c(1:10, seq(20, 90, 10), seq(100, 200, 50)),
                           n.iter = 200) %>% 
  rename_with(.fn = ~gsub("u", "u.DF_EM.oracle", x = .x, fixed = T), 
              .cols = starts_with("u")) %>% 
  rename(supertile.id.num = j, prior.DF_EM.oracle = i.u) %>%
  right_join(area$area.df.complete, by = "supertile.id.num") %>% 
  group_by(supertile.id) %>% 
  mutate(across(starts_with("u"), ~ . / n())) %>% 
  ungroup() %>% 
  dplyr::select(tile.id, starts_with("u"))


## DF equal

DF.equal.est <- DF_est(c.vec.dt = c.vec.dt, 
                       P.star.spm = P.star.equal.supertile.spm, 
                       a.supertile.vec = a.equal.supertile.helper)
DF.equal.est.dt <- data.table(j = as.numeric(names(a.equal.supertile.helper)),
                              u = DF.equal.est) %>%
  .[, u := fifelse(u < 1, 1, u)] # set negative values immediately to 0 or 1

## Renormalizing with EM and bringing estimate on tile.id level
DF_EM.equal.est <- EM_est(c.vec.dt = c.vec.dt, 
                          P.dt = P.star.equal.supertile.dt, 
                          a.vec.dt = DF.equal.est.dt,
                          selected.range = c(1:10, seq(20, 90, 10), seq(100, 200, 50)),
                          n.iter = 200) %>% 
  rename_with(.fn = ~gsub("u", "u.DF_EM.equal", x = .x, fixed = T), 
              .cols = starts_with("u")) %>% 
  rename(supertile.equal.id.num = j, prior.DF_EM.equal = i.u) %>%
  right_join(area$area.df.complete, by = "supertile.equal.id.num") %>% 
  group_by(supertile.equal.id) %>% 
  mutate(across(starts_with("u"), ~ . / n())) %>% 
  ungroup() %>% 
  dplyr::select(tile.id, starts_with("u"))
```


# DF estimator with iterations and dynamic threshold (T/k)
```{r}
DF_iterator.oracle.est <- DF_est_iterated(c.vec.dt = c.vec.dt, 
                                          P.star.spm = P.star.oracle.supertile.spm, 
                                          a.supertile.vec = a.supertile.helper, 
                                          P.dt = P.star.oracle.supertile.dt, 
                                          DF.threshold = 1,
                                          selected.range = c(1:10, seq(20, 90, 10), seq(100, 200, 50)),
                                          n.iter.DF = 200) %>% 
  rename_with(.fn = ~gsub("u", "u.DF_iterator.oracle", x = .x, fixed = T), 
              .cols = starts_with("u")) %>% 
  rename(supertile.id.num = j, prior.DF_iterator.oracle = prior) %>%
  right_join(area$area.df.complete, by = "supertile.id.num") %>% 
  group_by(supertile.id) %>% 
  mutate(across(starts_with("u"), ~ . / n())) %>% 
  ungroup() %>% 
  dplyr::select(tile.id, starts_with("u"))


# DF_iterator.equal.est <- DF_est_iterated(c.vec.dt = c.vec.dt, 
#                                          P.star.spm = P.star.equal.supertile.spm, 
#                                          a.supertile.vec = a.equal.supertile.helper, 
#                                          P.dt = P.star.equal.supertile.dt, 
#                                          DF.threshold = 1,
#                                          selected.range = c(1:10, seq(20, 90, 10), seq(100, 200, 50)),
#                                          n.iter.DF = 200) %>% 
#   rename_with(.fn = ~gsub("u", "u.DF_iterator.equal", x = .x, fixed = T), 
#               .cols = starts_with("u")) %>% 
#   rename(supertile.equal.id.num = j, prior.DF_iterator.equal = prior) %>%
#   right_join(area$area.df.complete, by = "supertile.equal.id.num") %>% 
#   group_by(supertile.equal.id.num) %>% 
#   mutate(across(starts_with("u"), ~ . / n())) %>% 
#   ungroup() %>% 
#   dplyr::select(tile.id, starts_with("u"))

```

# Putting all estimates together
```{r}
final.estimates.sf <- area$area.sf %>% 
  left_join(VOR.tower.est, by = "tile.id") %>% 
  left_join(VOR.offset.est, by = "tile.id") %>% 
  left_join(VOR.hotpoint.est, by = "tile.id") %>% 
  left_join(VOR.barycenter.est, by = "tile.id") %>% 
  left_join(SB.equal.est, by = "tile.id") %>%
  left_join(SB.oracle.est, by = "tile.id") %>%
  left_join(EM.equal.est, by = "tile.id") %>%
  left_join(EM.oracle.est, by = "tile.id") %>% 
  left_join(DF_EM.equal.est, by = "tile.id") %>% 
  left_join(DF_EM.oracle.est, by = "tile.id") %>% 
  # left_join(DF_iterator.equal.est, by = "tile.id") %>% 
  left_join(DF_iterator.oracle.est, by = "tile.id") 
  
final.estimates.df <- final.estimates.sf %>% 
  st_drop_geometry()

names.estimates <- final.estimates.sf %>% 
  # dplyr::select(pop, starts_with("u.")) %>% # all estimates
  dplyr::select(pop, matches("VOR|u.SB|oracle200|equal200")) %>% # only specific ones for mapping
  st_drop_geometry() %>% 
  names() 

```



# Evaluation

## Density plots

```{r}

# calculate density dataset for all estimates and GTP 
cdf.compare <- final.estimates.df %>% 
  dplyr::select(tile.id, all_of(names.estimates)) %>% 
  pivot_longer(cols = -tile.id, names_to = "estimates", values_to = "values") %>% 
  split(.$estimates) %>% 
  map(~custom_ecdf_prep(.)) %>% 
  map(~dplyr::select(., cum.prob.comp, pop.plot)) %>%
  map(~mutate(., cum.prob.comp = round(cum.prob.comp, 3))) %>% # effective plot sample --> faster plotting excluding overplot
  map_dfr(~distinct(.), .id = "type")
  

# ECCDF plot
(ECCDF.pop.plot <- cdf.compare %>% 
    ggplot() + 
    geom_line(aes(x = pop.plot, y = cum.prob.comp,
                  color = type), size = 1) + 
    scale_color_ptol() +
    scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
    scale_x_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
    annotation_logticks(sides = "lb") +
    labs(title = "ECCDF of estimators and GTP", y = "log10(ECCDF)", x = "log10(Mobile phones)",  
         colour = "") +
    theme(legend.position = "bottom"))
  
ggsave("eccdf.estimates.png", ECCDF.pop.plot, device = "png")

# ECDF.pop.plot <- ECDF.df %>%   
  #   ggplot() + 
  #   geom_point(aes(x = pop.plot, y = cum.prob.comp,
  #                  color = type
  #                  )) + 
  #   scale_color_ptol() +
  #   xlim(0, 30) +
  #   labs(title = "", y = "", x = "") +
  #   theme(legend.position = "none",
  #         plot.margin = unit(c(-0.5, 0, 0, -0.5), "cm")) 
  
  
  # combined <- ECCDF.pop.plot +
  #   annotation_custom(ggplotGrob(ECDF.pop.plot), 
  #                     xmin = 0, xmax = 1.5, 
  #                     ymin = min(ECCDF.df$log10.cum.prob.comp, na.rm = T), ymax = -1.5)
```


## Spatial density evaluation

```{r}

maps.labels <- list("GTP   ", "VOR_t ", "VOR_o ", "VOR_h ", "VOR_b ", "SB_e  ", "SB_o  ", 
                    "EM_e  ", "EM_o  ", "DF_EMo", "DF_EMe", "DF_DFo")

# check if there is divergence, what are the maximum estimates per tile for each estimator
max.maps <- final.estimates.sf %>% 
  st_drop_geometry() %>% 
  dplyr::select(tile.id, pop, matches("VOR|u.SB|oracle200|equal200")) %>% # only specific ones for mapping
  summarise_all(max) %>% 
  pivot_longer(cols = -tile.id, names_to = "estimator", values_to = "estimate")


# Define break points for discretized spatial density plots
breaks <- c(0, 2, 10, 20, 50, 100, 200, 500, 1000, Inf)
maps.input <- final.estimates.sf %>% 
  dplyr::select(tile.id, pop, all_of(names.estimates)) %>% 
  mutate(across(c(pop, starts_with("u.")), ~cut(., breaks = breaks, dig.lab = 7, right = F)))
  # mutate(across(c(pop, starts_with("u.")), ~log10(. + 1)))

# Build plots
(maps.estimation.density <- names.estimates %>%
  map2(., maps.labels, ~map_density(data = maps.input, var = .x, label = .y)) %>%
  set_names(names.estimates))

ggsave("Maps/pop.png", maps.estimation.density$pop, device = "png")
ggsave("Maps/u.VOR.tower.png", maps.estimation.density$u.VOR.tower, device = "png")
ggsave("Maps/u.VOR.offset.png", maps.estimation.density$u.VOR.offset, device = "png")
ggsave("Maps/u.VOR.hotpoint.png", maps.estimation.density$u.VOR.hotpoint, device = "png")
ggsave("Maps/u.VOR.barycenter.png", maps.estimation.density$u.VOR.barycenter, device = "png")
ggsave("Maps/u.SB.equal.png", maps.estimation.density$u.SB.equal, device = "png")
ggsave("Maps/u.SB.oracle.png", maps.estimation.density$u.SB.oracle, device = "png")
ggsave("Maps/u.EM.equal200.png", maps.estimation.density$u.EM.equal200, device = "png")
ggsave("Maps/u.EM.oracle200.png", maps.estimation.density$u.EM.oracle200, device = "png")
ggsave("Maps/u.DF_EM.equal200.png", maps.estimation.density$u.DF_EM.equal200, device = "png")
ggsave("Maps/u.DF_EM.oracle200.png", maps.estimation.density$u.DF_EM.oracle200, device = "png")
ggsave("Maps/u.DF_DF.oracle200.png", maps.estimation.density$u.DF_EM.oracle200, device = "png")

```

## KWD evaluation 

### Prep

```{r}

# define additional necessary rescalings of the area (next to 1x1)
rescale.factor.list <- list(area.2x2 = 2, 
                            area.4x4 = 4, 
                            area.8x8 = 8)

# aggregate estimate values based on rescaling level
area.rescaled.grid <- map(rescale.factor.list, 
            ~st_make_grid(area$area.sf, cellsize = area$area.params[["base.tile.size"]] * .x))
```


### KWD all estimates 2x2

```{r}
kwd.helper.est <- final.estimates.sf %>% 
  dplyr::select(-c(elevation, type)) %>%
  mutate(u.flat = mean(pop)) %>% 
  aggregate(by = area.rescaled.grid$area.2x2, FUN = sum, join = st_contains) %>%
  mutate(lon = map_dbl(geometry, ~st_centroid(.x)[[1]]),
         lat = map_dbl(geometry, ~st_centroid(.x)[[2]])) %>% 
  st_drop_geometry()

coordinates <- kwd.helper.est %>% 
  dplyr::select(lon, lat) %>% 
  as.matrix()

weights <- kwd.helper.est %>% 
  dplyr::select(pop, matches("u.")) %>% 
  as.matrix()

kwd.final <- compareOneToMany(coordinates, weights, L = 3, recode = TRUE)
cat("runtime:", kwd.final$runtime, " distance:", kwd.final$distance, " nodes:", 
    kwd.final$nodes, "arcs:", kwd.final$arcs, "\n")

names.weights <- colnames(weights)[-1]

kwd.eval <- tibble(estimator = names.weights,
                   kwd = kwd.final$distance * rescale.factor.list$area.2x2) %>%  # rescaling according to scale
  mutate(kwd.lower.bound = kwd - ((kwd / 100) * 1.29)) %>%  # for L=3 within 1 percent 
  mutate(iteration = str_extract(estimator, "[[:digit:]]+"),
         kind = str_extract(estimator, "[[:alpha:][:punct:]]+")) %>%
  mutate(iteration = case_when(is.na(iteration) ~ 0,
                               TRUE ~ as.numeric(iteration))) %>% 
  mutate(time.var = as.numeric(iteration) * 1,
         time.fix = case_when(str_detect(kind, "DF") ~ 3,
                              str_detect(kind, "u.EM") ~ 0)) %>%  # 11 min MP inverse
  mutate(time.final = (time.var + time.fix)) %>%
  group_by(kind) %>% 
  mutate(min.kwd.kind = min(kwd),
         kind.group = row_number() / max(row_number())) %>% # find minimum per estimator (for ordering help)
  ungroup() %>% 
  arrange(desc(min.kwd.kind), iteration) %>% 
  mutate(final.order = row_number()) %>% 
  mutate(estimator.new = factor(final.order, labels = estimator))
```
#### KWD 2x2 final estimates

```{r}
flat.ref.2x2 <- round(as.numeric(kwd.eval[kwd.eval$estimator == "u.flat", "kwd"]), 2)

(kwd.final.estimates.plot.2x2 <- kwd.eval %>% 
    filter(kind.group == 1,
           !str_detect(estimator, "flat|prior")) %>% 
    ggplot(aes(x = estimator.new, y = kwd, fill = kind, alpha = kind.group)) + 
    geom_bar(stat = "identity", position = position_dodge(width = 0.9)) + 
    geom_errorbar(aes(ymin = kwd.lower.bound, ymax = kwd), position = dodge, width = 0.25) +
    geom_text(aes(x = estimator.new, y = kwd, label = round(kwd, 2)), 
              position = position_dodge(0.1), hjust = -0.1, color = "Black", size = 3) +
    scale_alpha(range = c(0.5, 1), 
                guide = F
                # labels = unique(kwd.eval$iteration)
                ) + # noch ändern
    scale_fill_ptol(guide = FALSE) +
    coord_flip() +
    labs(x = "", y = "KWD", 
         alpha = "Iteration", 
         subtitle = paste0("(Reference: Flat = ", flat.ref.2x2, ")")) + 
    theme(legend.position = "bottom"))

ggsave(filename = "kwd final/kwd.final.estimates.2x2.plot.png", plot = kwd.final.estimates.plot.2x2, device = "png")
```






### KWD 1x1
needs adjustment and takes long to run

```{r}
# # KWD evaluation
# 
# rescale.factor <- 1
# 
# # area.2x2 <- area$area.sf %>% 
# #   dplyr::select(tile.id, pop) %>% 
# #   st_make_grid(cellsize = area$area.params[["base.tile.size"]] * rescale.factor)
# 
# kwd.helper.est <- final.estimates.sf %>% 
#   # dplyr::select(tile.id, pop, starts_with("u.")) %>% 
#   dplyr::select(tile.id, all_of(names.estimates)) %>%
#   mutate(u.flat = mean(pop)) %>% 
#   # aggregate(by = area.2x2, FUN = sum, join = st_contains) %>% 
#   mutate(lon = map_dbl(geometry, ~st_centroid(.x)[[1]]),
#          lat = map_dbl(geometry, ~st_centroid(.x)[[2]])) %>% 
#   st_drop_geometry()
# 
# coordinates <- kwd.helper.est %>% 
#   dplyr::select(lon, lat) %>% 
#   as.matrix()
# 
# weights <- kwd.helper.est %>% 
#   dplyr::select(pop, matches("u.")) %>% 
#   as.matrix()
# 
# kwd.final <- compareOneToMany(coordinates, weights, L = 3, recode = TRUE)
# cat("runtime:", kwd.final$runtime, " distance:", kwd.final$distance, " nodes:", 
#     kwd.final$nodes, "arcs:", kwd.final$arcs, "\n")
# 
# names.weights <- colnames(weights)[-1]
# kwd.eval <- tibble(estimator = names.weights,
#                    kwd = kwd.final$distance * rescale.factor) %>%  # rescaling according to scale
#   mutate(kwd.lower.bound = kwd - ((kwd / 100) * 1.29)) %>%  # for L=3 within 1 percent 
#   mutate(iteration = str_extract(estimator, "[[:digit:]]+"),
#          kind = str_extract(estimator, "[[:alpha:][:punct:]]+")) %>%
#   mutate(iteration = case_when(is.na(iteration) ~ 0,
#                                TRUE ~ as.numeric(iteration))) %>% 
#   group_by(kind) %>% 
#   mutate(min.kwd.kind = min(kwd),
#          kind.group = row_number() / max(row_number())) %>% # find minimum per estimator (for ordering help)
#   ungroup() %>% 
#   arrange(desc(min.kwd.kind), iteration) %>% 
#   mutate(final.order = row_number()) %>% 
#   mutate(estimator.new = factor(final.order, labels = estimator))
# 
# flat.ref <- round(as.numeric(kwd.eval[kwd.eval$estimator == "u.flat", "kwd"]), 2)
# 
# dodge <- position_dodge(width = 0.9)
# 
# (kwd.complete.plot <- kwd.eval %>% 
#     filter(kind.group == 1,
#            !str_detect(estimator, "flat")) %>% 
#     ggplot(aes(x = estimator.new, y = kwd, fill = kind, alpha = kind.group)) + 
#     geom_bar(stat = "identity", position = dodge) + 
#     geom_errorbar(aes(ymin = kwd.lower.bound, ymax = kwd), position = dodge, width = 0.25) +
#     geom_text(aes(x = estimator.new, y = kwd, label = round(kwd, 2)), 
#               position = position_dodge(0.1), hjust = -0.1, color = "Black", size = 3) +
#     scale_alpha(range = c(0.5, 1), 
#                 guide = F
#                 # labels = unique(kwd.eval$iteration)
#                 ) + # noch ändern
#     scale_fill_ptol(guide = FALSE) +
#     coord_flip() +
#     labs(x = "", y = "KWD", 
#          alpha = "Iteration", 
#          subtitle = paste0("(Reference: Flat = ", flat.ref, ")")) + 
#     theme(legend.position = "bottom"))
# 
# ggsave(filename = "kwd final/kwd.complete.1x1.plot.png", plot = kwd.complete.plot, device = "png")
```

#### kwd convergence (EM and DF)

```{r}

kwd.eval.convergence <- kwd.eval %>% 
  filter(!iteration == 0)

(kwd.convergence.plot.log.text <- kwd.eval.convergence %>% 
    dplyr::select(estimator, kwd, kwd.lower.bound, iteration, kind) %>% 
    ggplot(aes(x = iteration, y = kwd)) +
    geom_line(aes(color = kind)) +
    geom_point(aes(color = kind)) +
    geom_ribbon(aes(ymin = kwd.lower.bound, ymax = kwd, group = kind), alpha = 0.2) +
    geom_text_repel(aes(color = kind, label = round(kwd, 2)), size = 3, show.legend  = F) +
    scale_x_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
    annotation_logticks(sides = "b") +
    labs(color = "Estimator",
         x = "Iteration",
         y = "KWD"))


ggsave("kwd convergence/kwd.2x2.convergence.png", kwd.convergence.plot.log.text, device = "png")


(time.convergence.plot <- kwd.eval.convergence %>% 
    dplyr::select(estimator, time.final, iteration, kind) %>% 
    ggplot() +
    geom_line(aes(x = iteration, y = time.final, color = kind)) +
    geom_point(aes(x = iteration, y = time.final, color = kind)) +
    scale_color_discrete(breaks = c("u.DF_EM.oracle", "u.EM.oracle"), labels = c("DF", "EM")) +
    labs(color = "Estimator",
         x = "Iteration",
         y = "Time in seconds"))
  
ggsave("kwd convergence/time.png", time.convergence.plot, device = "png")

```



 continue here
# rescaling level evaluation


```{r}

names.order.estimator <- c("u.flat", 
                           "u.VOR.tower", "u.VOR.offset", "u.VOR.hotpoint", "u.VOR.barycenter",
                           "u.SB.equal", "u.SB.oracle",
                           "u.EM.equal", "u.EM.oracle", 
                           "u.DF_EM.equal", "u.DF_EM.oracle",
                           "u.DF_DF.oracle", "u.DF_DF.equal")

# define additional necessary rescalings of the area (next to 1x1)
rescale.factor.list <- list(area.1x1 = 1,
                            area.2x2 = 2, 
                            area.4x4 = 4, 
                            area.8x8 = 8)

# aggregate estimate values based on rescaling level
area.rescaled.grid <- map(rescale.factor.list, 
            ~st_make_grid(area$area.sf, cellsize = area$area.params[["base.tile.size"]] * .x))


mse.relevant.estimators <- final.estimates.sf %>% 
  dplyr::select(tile.id, pop, matches("VOR|SB|flat|1|10|100|200")) %>% 
  dplyr::select(-matches("prior"))
  

mse.est <- map(area.rescaled.grid, ~aggregate(mse.relevant.estimators, by = .x, FUN = mean, join = st_contains)) %>% 
  map(~st_drop_geometry(.))

point <- mse.est %>% 
  map(~mutate(., tile.id.rescaled = row_number())) %>% 
  map(~dplyr::select(., tile.id.rescaled, pop, starts_with("u."))) %>% 
  map_dfr(~pivot_longer(., cols = -c(tile.id.rescaled, pop), 
                        names_to = "estimator", values_to = "estimate"), .id = "scale") %>% 
  mutate(rescale.factor = as.numeric(str_extract(scale, "[[:digit:]]")),
         iteration = str_extract(estimator, "[[:digit:]]+"),
         kind = str_extract(estimator, "[[:alpha:][:punct:]]+")) %>% 
  mutate(iteration = case_when(is.na(iteration) ~ 0,
                               TRUE ~ as.numeric(iteration))) %>% 
  mutate(estimator.ordered = factor(kind, levels = names.order.estimator))


# selected estimators (iterations) for 2d density plots
scatter.names <- c("u.EM.oracle1", "u.EM.oracle10", "u.EM.oracle100", "u.EM.oracle200",
                   "u.VOR.barycenter", "u.VOR.tower")

scatter.density.plots <- scatter.names %>% 
  map(~scatter_density(point, estimator.name = .x)) %>%
  set_names(scatter.names)

ggsave("2d_density/u.EM.oracle1.density.png", scatter.density.plots$u.EM.oracle1, device = "png")
ggsave("2d_density/u.EM.oracle10.density.png", scatter.density.plots$u.EM.oracle10, device = "png")
ggsave("2d_density/u.EM.oracle100.density.png", scatter.density.plots$u.EM.oracle100, device = "png")
ggsave("2d_density/u.EM.oracle200.density.png", scatter.density.plots$u.EM.oracle200, device = "png")
ggsave("2d_density/u.VOR.barycenter.png", scatter.density.plots$u.VOR.barycenter, device = "png")
ggsave("2d_density/u.VOR.tower.png", scatter.density.plots$u.VOR.tower, device = "png")



```


